---
title: "Homework 5"
author: "Chris Ballenger"
date: "6/5/2018"
output: 
    html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quesiton 1 Data Munging

#### a) Import and add column names
```{r echo=TRUE}
df <- read.table('data/yob2016.txt',sep=';',header = FALSE)
names(df) <- c('name','gender','total_kids')
head(df)
```

#### b) Summary & Structure
Summary
```{r echo=TRUE}
summary( df )
```
Structure
```{r echo=TRUE}
dim( df )
str( df )
```

#### c) Search for a specific name
```{r echo = TRUE}
df[grep('yyy$', df[,1]),]
```

#### d) remove value and create new dataset
```{r echo = TRUE}
y2016 <- df[-grep('yyy$', df[,1]),]
```

## Question 2 Data Merging
#### a) Import and add column names for yob2015
```{r echo = TRUE}
y2015 <- read.table('data/yob2015.txt',sep=',',header = FALSE)
names(y2015) <- c('name','gender','total_names_2015')
head(y2015)
```

#### b) Display last 10 rows
The most uncomon names all start with Z
```{r echo = TRUE}
tail(y2015, 10)
```

#### c) Merge y2016 & y2015
```{r echo = TRUE}
# Merge Data
result <- merge(y2015, y2016, by.x = 'name', by.y = 'name')
# Update Names
names(result) <- c('name','gender_2015','total_counts_2015','gender_2016','total_counts_2016')
head(result)

# Validate no NAs
sapply(result, function(x) sum(is.na(x)))
```

## Question 3
#### a) Total the total_counts_yyyy columns and sum all values
```{r echo = TRUE}
result$total_counts_all <- result$total_counts_2015 + result$total_counts_2016
#Total children
sum(result$total_counts_all)
```

#### b) Show top 10 most popular names
```{r echo = TRUE}
result <- result[order(result$total_counts_all, decreasing = TRUE),]
head(result, 10)
```

#### c) Show only girl names
```{r echo = TRUE}
girl_names <- result[which(c(result$gender_2015=='F',result$gender_2016=='F')),]
head(girl_names)
```

#### d) Write to csv file data/top_10_girl_names.csv
```{r eval = FALSE, echo= TRUE}
write.csv(head(girl_names[,c(1,6)],10), file='data/top_10_girl_names.csv', row.names = FALSE)
```

## Question 4) Upload to GitHub
https://github.com/toadies/Homework_6306/tree/master/Assignment5

