---
title: "Homework 11"
author: "Chris Ballenger"
date: "7/25/2018"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(kableExtra)
library(ggplot2)
library(fpp2) 
library(dygraphs)
library(xts)
```

#### Question 1: Brief Financial Data
##### a) Attain DAX Index
```{r}
daxIndex <- EuStockMarkets[,"DAX"]
str(daxIndex)
```

##### b) Plot the Dax Index
```{r}
plot(
    daxIndex,
    main="EU DAX Index from 1850 to Current",
    xlab="Year",
    ylab="Index Price",
    col="blue"
)
abline(
    v=1997,
    color="red"
)
```

##### c) Decomposed DAX Index
```{r}
daxIndex.decompose.multi <- decompose(daxIndex,type="multiplicative")
plot(daxIndex.decompose.multi,col="blue")
abline(
    v=1997,
    col="red"
)
```

#### Question 2: Temperature Data
##### a) Attain maxtemp data set
```{r}
autoplot(maxtemp)
```

##### b) Get temps from 1990 to current
```{r}
temps <- window(maxtemp, start = 1990)
```

##### c) Predict next 5 years
```{r}
temps.ses <- ses(
    temps, 
    h=5
)
plot(temps.ses)
lines(
    temps.ses$fitted,
    col="blue"
)
temps.ses$model$aicc
```

##### d) Holt's Linear Trend
```{r}
temps.holt <- holt(
    temps, 
    h=5, 
    damped = TRUE, 
    inital = "optimal"
)
plot(temps.holt)
lines(
    temps.holt$fitted,
    col="blue"
)

temps.holt$model$aicc
```

##### e) Compare AICc
```{r}
temps.ses$model$aicc
temps.holt$model$aicc
```
The model with the best fit is SES.

#### Question 3: The Wands Choose the Wizard
##### a) Load Data
```{r}
gregorovitch <- read.csv("Unit11TimeSeries_Gregorovitch.csv")
ollivander <- read.csv("Unit11TimeSeries_Ollivander.csv")

names(gregorovitch) <- c("year","wands_sold")
names(ollivander) <- c("year","wands_sold")

str(gregorovitch)
str(ollivander)
```

##### b) Format Date
```{r}
gregorovitch$year <- as.Date(gregorovitch$year, "%m/%d/%Y")
ollivander$year <- as.Date(gregorovitch$year, "%m/%d/%Y")

str(gregorovitch)
str(ollivander)
```

##### c) Load data into time series
```{r}
gregorovitch.ts <- xts(gregorovitch$wands_sold, order.by=gregorovitch$year)
ollivander.ts <- xts(ollivander$wands_sold, order.by=ollivander$year)
str(gregorovitch.ts)
str(ollivander.ts)
```

##### d) Create a dyGraph
```{r}
wandsSold <- merge(gregorovitch.ts,ollivander.ts)

dygraph(wandsSold,main="Olivander vs. Gregorovitch Wand Sales",xlab="Year",ylab="Sales") %>%
    dySeries("ollivander.ts", label="Ollivander", col="red") %>%
    dySeries("gregorovitch.ts", label="Gregorovitch",col="green") %>%
    dyRangeSelector() %>%
    dyShading(from="1995-01-01",to="1999-01-01") %>%
    dyHighlight(highlightSeriesOpts = list( strokeWidth = 3 ) )