---
title: "Homework 10"
author: "Chris Ballenger"
date: "7/17/2018"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(kableExtra)
library(ggplot2)
```

#### Question 1 Mental Helath Clinics (40%)
##### a) Load Data from N-MHSS
```{r}
load("N-MHSS-2015-DS0001-bndl-data-r/N-MHSS-2015-DS0001-data/N-MHSS-2015-DS0001-data-r.rda")

# Clean White spaces on LST
levels(mh2015_puf$LST) <- trimws(levels(mh2015_puf$LST))

str(mh2015_puf)
```

##### b) Distinct List of States
```{r}
states <- unique(mh2015_puf$LST)
kable( states,row.names=FALSE )  %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F)
```

##### c) Filter for VAs
```{r}
va <- mh2015_puf[mh2015_puf$FACILITYTYPE == "Veterans Administration medical center (VAMC) or other VA health care facility",]
va <- va[va$LST != "AK" & va$LST != "HI" & va$LST != "PR" & va$LST != "VI" & va$LST != "AS",c(1,2)]

va.states <- va %>%
    group_by(LST) %>%
    summarize(count = n())
kable( va.states,row.names=FALSE )  %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F)
```

##### d) Bar Graph
```{r fig.height=10}
ggplot( va.states , aes( LST, count, fill = LST ) ) +
    geom_bar(stat="identity") +
    labs(title="Veterans Affairs Centers by State",y ="Total Medical Centers", x = "State") +
    coord_flip() +
    theme(plot.title = element_text(hjust = 0.5))
```

#### 2) Cleaning and Bringing in New Features (60%)
##### a)  Bring in Area
```{r}
s <- data.frame(abb = state.abb, area = state.area, region = state.region, name = state.name)
va.states <- merge(va.states, s, by.x="LST",by.y="abb", all.x=TRUE)
kable(head( va.states ),row.names=FALSE )  %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F)
```

All states match with the exception of DC.  This is because I used the states.abb table and not include District of Columbia.  The join also works because I did a tidy data initially to remove white spaces on LST to help filter.

##### b) Correction
No correction required, we will not report square miles of DC.

##### c) Calcualte per 1000 sq miles
```{r}
va.states$per_sq_mile <-  va.states$area / va.states$count / 1000
kable(head( va.states ),row.names=FALSE )  %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F)
```

##### d) Bar Chart
```{r}
ggplot( va.states[!is.na(va.states$per_sq_mile),]  , aes( x = reorder(name, per_sq_mile ), per_sq_mile, fill = region ) ) +
    geom_bar(stat="identity") +
    labs(title="Veterans Affairs Centers by State",y ="Total Medical Centers per 1000 sq miles", x = "State") +
    coord_flip() +
    theme(plot.title = element_text(hjust = 0.5))

```

##### e) Analysis
The West Region has the highest VA medical centers per 1000 sq miles.  While the Northeast has the least.  Before making a decision, we need to include population to determine if the Northeast is the right fit for a new Medical Center.